Sparse Function-space Representation \\ of Neural Networks

### 2023-05-16 paper/main.tex
Minor fixes in CL

\paragraph{\our for continual learning}
% Definition of CL -> a sequence of tasks 
In the continual learning setting, the training is divided into $T$ tasks, each with its training data set $\dataset_t = \{(\mathbf{x}_{i}, \mathbf{y}_{i})\}_{i=1}^{N_t}$, which after the task is discarded and cannot be accessed in the following stages of the training. Rehearsal and function regularization-based models keep a subset of the training data for each task to help the model alleviate forgetting. In the same way, after each task, we can use our \our method to build a compact representation of the neural network and then exploit this representation to build a functional regularizer to add to the training loss for the subsequent tasks. Recently proposed GP-based regularizers \cite{ pan2020continual, rudner2022continual} have shown better performances than weight space equivalents getting state-of-the-art on CL benchmarks. However, they are limited to use subset approximations of the posterior \cref{app:cl-experiment}.
%, which in practice means randomly selecting some data computing its posterior at only those points and then using that as the regularizer. 
A more principled approach would be to sparsify the resultant GP into a low-rank approximation to ensure information coming from the entire task dataset is not lost. %, essentially what the sparse dual variables do.   \todo{this term is replacing the missing data}
% Where the regularizer comes from
At the end of the training for each task $t$, we compute the Laplace-GGN approximated kernel function for the current model and randomly select $M$ inducing points. Given the issues described in the previous sections, related to computing the full covariance posterior $\MKxx$ for $\dataset_t$,\todo{this should be $\kappa(\MX_t, \MX_t)$} we can exploit the dual parameterization to efficiently encode the information from  $\dataset_t$ using the dual parameterization, as follows, 
%
\begin{equation}\textstyle
 	\bar{\MB}^{-1}_t = \MKzz^{-1} \MBeta_\vu \MKzz^{-1} \in \R^{M \times M}, 
 	\quad \text{s.t.} \quad
 	\MBeta_{\vu} =  \sum_{i \in \dataset_t} \vkzi \,\hat{\beta}_{i} \, \vkzi^{\T} ,    
 	% \quad \forall t \in [1, T]
\end{equation}
%
where $\MKzz$ and $\vkzi$ are the gram matrix and vector computed on the inducing points $\mathcal{Z}_t = \{\vz_i\}_{i=1}^M$ selected from $\dataset_t$.\
%
We keep a memory buffer $\mathcal{M} = \{(\mathcal{Z}_t, \vu_t, \bar{\MB}^{-1}_t)\}_{t=1}^T$, where $\vu_t \in \R^{M}$ is a vector with entries $u_{t, i} = f_{\vw_t^*}(\vz_i), \forall \vz_i \in \mathcal{Z}_t$ are the neural network outputs computed on the inducing points with the MAP estimate $\weights_t^*$ after task $t$. For notational convenience, we restrict here to single-output neural networks and refer the reader to further details on the multi-output setting to \cref{sec:cl_multioutput}.

After each task, we update $\mathcal{M}$, and we can construct a regularizer term, which aims to reduce the drift of the current model from diverging on the inducing points $\MZ_s$ for all previous tasks $ s = 1, \ldots, t-1$. This means that for training  the successive task, the new objective to minimize becomes $\weights_t^* = \arg\min_{\weights} \mathcal{L}(\mathcal{D}_t, \weights) + \tau \, \mathcal{R}_\textrm{\our}(\weights, \mathcal{M})$, with weight $\tau$ and regularizer
%
\begin{equation}\label{eq-cl-regularizer}\textstyle
  \mathcal{R}_\mathrm{\our}(\weights, \mathcal{M}) = \frac{1}{2} \sum_{s=1}^{t-1} \frac{1}{M} 
	\left\lVert 
	\vu_t - \vu_s % f_{\weights_{s}}(\MZ_s)
	\right\rVert_{\bar{\MB}^{-1}_{s}}, \quad \vu_t \in \R^M, \text{with } u_{s,i} = f_{\weights}(\vz_{i}) \forall {\vz_i} \in \mathcal{Z}_s .
\end{equation}

>>>>

\paragraph{\our for continual learning}
% Definition of CL -> a sequence of tasks 
In the continual learning setting, the training is divided into $T$ tasks, each with its training data set $\dataset_t = \{(\mathbf{x}_{i}, \mathbf{y}_{i})\}_{i=1}^{N_t}$, which after the task is discarded and cannot be accessed in the following stages of the training. Rehearsal and function regularization-based models keep a subset of the training data for each task to help the model alleviate forgetting. In the same way, after each task, we can use our \our method to build a compact representation of the neural network and then exploit this representation to build a functional regularizer to add to the training loss for the subsequent tasks. Recently proposed GP-based regularizers \cite{ pan2020continual, rudner2022continual} have shown better performances than weight space equivalents getting state-of-the-art on CL benchmarks. However, they are limited to use subset approximations of the posterior \cref{app:cl-experiment}.
%, which in practice means randomly selecting some data computing its posterior at only those points and then using that as the regularizer. 
A more principled approach would be to sparsify the resultant GP into a low-rank approximation to ensure information coming from the entire task dataset is not lost. %, essentially what the sparse dual variables do.   \todo{this term is replacing the missing data}
% Where the regularizer comes from
At the end of the training for each task $t$, we compute the Laplace-GGN approximated kernel function for the current model and randomly select $M$ inducing points. Given the issues described in the previous sections, related to computing the full covariance posterior $\MKxx$ for $\dataset_t$,\todo{this should be $\kappa(\MX_t, \MX_t)$} we can exploit the dual parameterization to efficiently encode the information from  $\dataset_t$ using the dual parameterization, as follows, 
%
\begin{equation}\textstyle
 	\bar{\MB}^{-1}_t = \MKzz^{-1} \MBeta_\vu \MKzz^{-1} \in \R^{M \times M}, 
 	\quad \text{s.t.} \quad
 	\MBeta_{\vu} =  \sum_{i \in \dataset_t} \vkzi \,\hat{\beta}_{i} \, \vkzi^{\T} ,    
 	% \quad \forall t \in [1, T]
\end{equation}
%
where $\MKzz$ and $\vkzi$ are the gram matrix and vector computed on the inducing points $\mathcal{Z}_t = \{\vz_i\}_{i=1}^M$ selected from $\dataset_t$.\
%
We keep a memory buffer $\mathcal{M} = \{(\mathcal{Z}_t, \vu_t, \bar{\MB}^{-1}_t)\}_{t=1}^T$, where $\vu_t \in \R^{M}$ is a vector with entries $u_{t, i} = f_{\vw_t^*}(\vz_i), \forall \vz_i \in \mathcal{Z}_t$, are the neural network outputs computed on the inducing points with the MAP estimate $\weights_t^*$ after task $t$. For notational convenience, we restrict ourselves here to single-output neural networks and refer the reader to \cref{sec:cl_multioutput} for details on the multi-output setting.

After each task, we update $\mathcal{M}$, and we can construct a regularizer term, which aims to reduce the drift of the current model from diverging on the inducing points $\MZ_s$ for all previous tasks $ s = 1, \ldots, t-1$. This means that for training  the successive task, the new objective to minimize becomes $\weights_t^* = \arg\min_{\weights} \mathcal{L}(\mathcal{D}_t, \weights) + \tau \, \mathcal{R}_\textrm{\our}(\weights, \mathcal{M})$, with weight $\tau$ and regularizer
%
\begin{equation}\label{eq-cl-regularizer}\textstyle
  \mathcal{R}_\mathrm{\our}(\weights, \mathcal{M}) = \frac{1}{2} \sum_{s=1}^{t-1} \frac{1}{M} 
	\left\lVert 
	\vu_t - \vu_s % f_{\weights_{s}}(\MZ_s)
	\right\rVert_{\bar{\MB}^{-1}_{s}}, \quad \vu_t \in \R^M \text{~with~} u_{s,i} = f_{\weights}(\vz_{i}),~\forall {\vz_i} \in \mathcal{Z}_s .
\end{equation}
